A SAT-Based Counterexample Guided Method for Unbounded Synthesis

### 2016-01-26 paper.tex
Some more related work

Advances in SAT solving technology has prompted research into its applicability
to synthesis as an alternative to BDDs. One approach is to find sets of states
in CNF \cite{demiurge}. Another approach is to eschew states and focus on
\emph{runs} of the game. Previous work has applied this idea to realizability
of bounded games \cite{narodytska2014} by forming abstract representations of
the game.  In this paper, we extend this idea to unbounded games by
constructing approximate sets of winning states from abstract trees.

@@

By checking for the existence of a winning run for the environment in an
abstract game tree constructed from a partial controller strategy we are
checking if the partial strategy is winning. If no environment-winning run is
exists within the partial strategy then it is a winning partial strategy,
otherwise the spoiling run is a counterexample that proves that the partial
strategy is not winning. This forms the basis of a counterexample guided
abstraction refinement framework that operates on candidate strategies.

@@

>>>>

Advances in SAT solving technology has prompted research into its applicability
to synthesis as an alternative to BDDs. One approach is to find sets of states
in CNF \cite{bloem2014}. Another approach is to eschew states and focus on
\emph{runs} of the game. Previous work has applied this idea to realizability
of bounded games \cite{narodytska2014} by forming abstract representations of
the game.  In this paper, we extend this idea to unbounded games by
constructing approximate sets of winning states from abstract trees.

@@

By checking for the existence of a winning run for the environment in an
abstract game tree constructed from a partial controller strategy we are
checking if the partial strategy is winning. If no environment-winning run is
exists within the partial strategy then it is a winning partial strategy,
otherwise the spoiling run is a counterexample that proves that the partial
strategy is not winning. This forms the basis of a counterexample guided
abstraction refinement framework \cite{clarke2000} that operates on candidate strategies.

@@

Synthesis of safety games is a thoroughly explored area of research with most
efforts directed toward solving games with BDDs \cite{burch1990} and abstract
interpretation \cite{walker2014,brenguier2014}. Satisfiability solving has been used
previously for synthesis in a suite of methods proposed by Bloem et al
\cite{bloem2014}. The authors propose a propose employing competing SAT solvers
to learn clauses, which is similar to our approach but does not unroll the
game. They also suggest QBF solver, template-based, and Effectively
Propositional Logic (EPL) approaches.

There are different approaches to bounded synthesis than the one described
here. The authors of \cite{finkbeiner2013} suggest a methodology directly
inspired by bounded model checking and it has been adapted to symbolic
synthesis \cite{ehlers2010}. Lazy synthesis \cite{finkbeiner2012} is a
counterexample-guided approach to bounded synthesis that refines an
implementation for the game instead of an abstraction of it.

SAT-based bounded model checking approaches that unroll the transition relation
have been extended to unbounded by using conflicts in the solver
\cite{mcmillan2002}, or by interpolation \cite{mcmillan2003}. However, there
are no corresponding adaptations to synthesis. Incremental induction
\cite{bradley2011} is another technique for unbounded model checking with an
equivalent synthesis method \cite{morgenstern2013}, which computes the set of
safe states incrementally.
